---
title: "Delphine_Assignment4.Rmd"
output: html_notebook
---
```{r}
library(tidyverse)
library (ggplot2)
```
importing data
```{r}
assignment4 = read_csv("a4_data.csv")
nrow(assignment4)
ncol(assignment4)
colnames(assignment4)
```
subset
```{r}
prime_information = assignment4%>%
  select(subject, prime_condition)
```


rows and columns - this has 3700 rows and 12 columns.

unique participants
```{r}
assignment4%>%
  group_by(subject)%>%
  count()
```
prime_information
```{r}
condition_data=assignment4%>%
  select(subject, prime_condition)
```
phonological
```{r}
phonological = assignment4%>%
filter(prime_condition == "phonological" &
       accuracy== 1)
```
subject acc
```{r}
subject_acc = assignment4%>%
  group_by(subject)%>%
summarize(mean_accuracy=mean(accuracy))
```
prime_acc
```{r}
prime_acc = assignment4%>%
  group_by(prime_condition)%>%
summarise(mean_accuracy=mean(accuracy),
          sd_accuracy=sd(accuracy))
```
#ggplot
```{r}
library(ggplot2)
library(ggthemes)
subject_acc%>%
  ggplot(aes(x=mean_accuracy))+
  geom_histogram(binwidth=0.2,
                 fill="purple", color="black",
                 position="identity")+
  theme_few()+
  xlab("mean accuracy")+
  ylab("Count")+
  ggtitle("Histogram of mean accuracy")

```
# bar graphs
```{r}
prime_acc%>%
  ggplot(aes(x=prime_condition, y=mean_accuracy))+
  geom_bar(stat="identity", fill="pink", color="magenta")+
  theme_fivethirtyeight()+
  xlab("prime condition")+
  ylab("mean accuracy")+
  ggtitle("Barplot of prime condition")
```
The pattern I am observing does show that type of prime condition causes a change in mean accuracy in the trivia experiment. More specifically, phonological prime condition leads to the most accuracy, and the semantic prime condition leads to the least amount of accuracy.